\documentclass[a4paper,10pt]{article}
% Modified margins from .5 across the board to .4 .4 .4 .5 because THOU SHALT BE ON 2 PAGES
\usepackage[left=.4in, right=.4in, top=.4in, bottom=.5in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{sectsty}
\usepackage{unnumberedtotoc}

% Custom formatting for addsecs and lists
\titleformat{\addsec}{\large\bfseries}{\thesection}{1em}{}
\setlist[itemize]{leftmargin=*, labelsep=5pt}
\begin{document}
% Header block
\begin{center}
    \textbf{\LARGE Michael Maldonado} \\
    7409 S. 177th St, NE 68136 \\
    605-760-7918 \\
    \href{mailto:michael@maldonado.tech}{michael@maldonado.tech} ||
    \href{https://linkedin.com/in/michaelcmaldonado}{linkedin.com/in/michaelcmaldonado} ||
    \href{https://github.com/punchy98}{github.com/punchy98}
\end{center}

\section*{Professional Summary}
Michael is a Cyber Security professional with a passion for Blue Team operations and continous learning. He has extensive experience in managing and remediating diverse cyber incidents, ranging from email account compromises to ransomware. Michael has a strong IT backgroud with expertise in Linux and Windows administration.
\section*{Skills}
\small
\begin{itemize}
    \begin{multicols}{2}
    \small
    \leftskip=4em
    \item Problem Solving and Extreme Googling
    \item Open Source Intelligence (OSINT)
    \item Windows and Linux administration/troubleshooting
    \item Effective and efficient performance under pressure
    \item Cyber Threat Intelligence
    \item Network Analysis and Threat Hunting
    \item Incident Response
    \item Security Orchestration, Automation, and Response (SOAR)
    \end{multicols}
\end{itemize}

\section*{Work History}
\begin{itemize}
    \item\textbf{Senior Security Response Engineer, 07/2024 - Present} \\
    Cloudera - Remote - Omaha, NE
    \begin{itemize}
        \small
        \leftskip=4em
        \item Performed proactive monitoring and reponse to security alerts and events from various sources (SIEM, Cloud Security Platforms, EDR)
        \item Conducted in-depth analysis of security incidents to determine the root cause and impact, and recommended appropriate mitigation strategies.
        \item Developed and maintained incident response playbooks, processes, and procedures to streamline response efforts and improve the organization's security posture.
        \item Conducted threat hunting activities to identify advanced threats
        \item Identified, documented, and researched Threat Intelligence findings and reports.
        \item Provided mentorship and guidance to junior analysts and engineers.
        \item Evaluated and implemented new security tools and technologies.
    \end{itemize}
    \item\textbf{Senior Cyber Security Engineer, 05/2023 - 07/2024} \\
    Union Pacific Railroad - Omaha, NE
    \begin{itemize}
        \small
        \leftskip=4em
        \item Lead the OT vulnerability management program to meet TSA directives for Class I Railroads
        \item Coordinated Proof of Concepts with OT security vendors and created success criteria
        \item Coordinated other teams to identify OT patching processes
        \item Facilitated access management reviews
        \item Acted as a mentor to new team members
        \item Continued all functions from previous role
    \end{itemize}
    \item\textbf{Cyber Security Engineer, 05/2022 - 05/2023} \\
    Union Pacific Railroad - Omaha, NE
    \begin{itemize}
        \small
        \leftskip=4em
        \item IT vulnerability management via Tenable (reporting, creating scans, deploying new scanners, etc)
        \item Security administration and troubleshooting for 14,000 Linux servers
        \item Scripted automated access management reporting in Python
        \item Created process documentation
        \item Acted as a mentor to new team members, helping with whatever they needed
        \item Lead our team's script conversion process going from Perl 5 to Python 3.9
    \end{itemize}
    \item\textbf{Cyber Security Specialist, 10/2020 - 05/2022} \\
    Marco Techologies - Omaha, NE
    \begin{itemize}
        \small
        \leftskip=4em
        \item Responded to and handled different types of incidents ranging from Office 365 account compromises to ransomware.
        \item Monitored logs in an ELK-based SIEM.
        \item Active threat hunting looking for indicators of attack that SIEM/EDR did not detect.
        \item Assisted clients with ongoing 3rd party audits and remediating the findings.
        \item Performed security assessments for clients aligned to the NIST Cyber Security Framework.
        \item Performed vulnerability scans, created remediation plans, and assisted with the remediation.
        \item Wrote scripts to automate various tasks, including O365 management.
        \item Served as a Cyber Security SME to clients.
    \end{itemize}
    \item\textbf{Rapid Resolution Technician, 07/2020 - 10/2020} \\
    Marco Techologies - Omaha, NE
    \begin{itemize}
        \small
        \leftskip=4em
        \item Served as a first line of defense for our Tier 1 helpdesk, dispatching tickets and calls.
    \end{itemize}
    \item\textbf{IT Support Specialist, 04/2020 - 07/2020} \\
    First Dakota National Bank - Sioux Falls, SD
    \begin{itemize}
        \small
        \leftskip=4em
        \item Provided exceptional support by promptly addressing and resolving user queries through support calls and help desk tickets, ensuring a seamless user experience.
        \item Installed and configured various equipment, ensuring seamless functionality and optimal performance.
        \item Automated routine tasks by developing PowerShell scripts, enhancing efficiency and reducing manual workload.
    \end{itemize}
    \item\textbf{Technology Intern, 05/2019 - 04/2020} \\
    Fishback Financial Corporation - Brookings, SD
    \begin{itemize}
        \small
        \leftskip=4em
        \item Provided exceptional support by promptly addressing and resolving user queries through support calls and help desk tickets, ensuring a seamless user experience.
        \item Demonstrated technical proficiency by efficiently installing equipment and managing the decommissioning process for virtual desktops, contributing to streamlined and optimized IT operations.
        \item Played a key role in the successful transition to Windows 10, providing valuable assistance in the conversion process and ensuring a smooth migration for end-users.
        \item Leveraged expertise in automation by creating and implementing time-saving PowerShell scripts, enhancing operational efficiency and reducing manual workload.
    \end{itemize}
\end{itemize}

\section*{Education}
\textbf{Bachelor of Science: Cyber Operations} \\
Dakota State University - Madison, SD
\section*{Professional Development and Certifications}
\href{https://www.credly.com/badges/87563fff-910c-449c-ab21-f571b162cd4b/public_url}{\textbf{GIAC Certified Intrusion Analyst (GCIA)}}\\
\href{https://arcx.io/verify-certificate?id=2991f7743ca358a0f528c32e6685a7f68ffcd332&k=387d43ca09294cb6a13b2ed95eccb859}{\textbf{arcX Cyber Threat Intelligence Practitioner}}\\
\href{https://certification.tines.com/certificate/qTQkd1xZ7Q}{\textbf{Tines Core Certification}}\\
\href{https://www.credly.com/badges/f1f32bab-c511-4114-b884-e69ae2506275/public_url}{\textbf{AWS Partner: AWS GovCloud (US) Essentials}}\\
\href{https://www.credly.com/badges/4c4eef78-ec4f-4911-ae68-dc4a4c811ba2/public_url}{\textbf{AWS Partner: Technical Accredited}}\\
\textbf{CISA ICS Cybersecurity Training}
\section*{Professional Organizations}
\textbf{Infragard - Nebraska Chapter} \\
\href{https://www.credly.com/badges/a65cec63-e07c-4e52-b154-842564aadf65/public_url}{\textbf{GIAC Advisory Board}}
\section*{Personal Projects:}
\begin{itemize}
\item\textbf{Homelab} \\
For 5+ years, I have been actively maintaining homelab which provides a space for continous learning and self-reliance in an attempt to free mine (and my family's) dependence on cloud hosted software. Below is an incomplete list of tools and technologies I use or have experimented with. For an up to date list of tools and technologies that I am running, please visit my GitHub page.\\
    \begin{itemize}
        \small
        \begin{multicols}{2}
        \item Containerization (Docker \& Podman)
        \item Automation \& Scripting (Ansible, Terraform, Python, Bash, Perl)
        \item Networking (Cisco NX-OS/IOS/ASA, TP-Link Omada SDN)
        \item Virtualization (ProxMox VE, KVM)
        \item Visualization \& Monitoring (Zabbix, Prometheus+Grafana)
        \item Linux (Ubuntu, RHEL 7+, OpenSUSE) and BSD (FreeBSD)
        \item Security Onion (Snort, Zeek, ELK, etc.)
        \end{multicols}
    \end{itemize}
%\item\textbf{Capture the Flags and OSINT Challenges} \\
%I have completed 10 machines (11 user owns and 10 system owns) and 11 Sherlocks on HackTheBox. I also participate in a
\end{itemize}
\end{document}
